Revised Interoceptive Accuracy Scale (IAS-R)

### 2024-02-20 analysis/analysis.qmd
add fig 1

@@

rbind(dens1, dens2, dens3, dens4, dens5, dens6, dens7) |>
  ggplot(aes(x = x, y = y, color = Parameter)) +
  geom_line() +
  theme_minimal() +
  labs(title = "Distribution of Responses", x = "Response", y = "Density", color = "Item") +
  facet_wrap(~Sample, scales = "free", nrow = 4)
```

@@

Limitations:
- Not much clear theorethical or empirical structure (small grouping of items)
- Limited variability (clear mode at 4/5)
- Ambiguous items which grouping depends on the context (and its awareness)
  - E.g., heart beating fast, vomit when nauseaous
- Few items for some modalities (e.g., 1 for heart)
- Positive phrasing: benefits but also might exacerbate positivity bias (and thus unidimensionality)

>>>>

The items with the differing distribution pattern (with a lower mode around 2/5) are "Affective Touch", "Blood Sugar" and "Bruise".

@@

p1 <- rbind(dens1, dens2, dens3, dens4, dens5, dens6, dens7) |>
  # mutate(Dashed = ifelse(Parameter %in% c("Affective_touch", "Blood_Sugar", "Bruise"), TRUE, FALSE)) |> 
  ggplot(aes(x = x, y = y, color = Parameter)) +
  geom_line() +
  scale_color_material_d() +
  scale_linetype_manual(values = c("solid", "dashed"), guide="none") +
  theme_minimal() +
  theme(axis.text.y = element_blank(),
        plot.title = element_text(face="bold", hjust=0.5)) +
  labs(title = "Distribution of responses for all items across various datasets", x = "Response", y = "Density", color = "Item") +
  facet_wrap(~Sample, scales = "free", nrow = 4)

ggsave("figures/Figure1.png", p1, width=10, height=10, dpi=200, bg="white")
p1
```

@@

Limitations:
- Not much clear theorethical or empirical structure (small grouping of items)
- Limited variability (clear mode at 4/5), very low prevalence of 5/5 responses.
- Ambiguous items which grouping depends on the context (and its awareness)
  - E.g., heart beating fast, vomit when nauseaous
- Few items for some modalities (e.g., 1 for heart)
- Positive phrasing: benefits but also might exacerbate positivity bias (and thus unidimensionality)
